---
title: "Jake's Homework #8"
output: html_document
---

```{r}
library(dplyr)
df <-read.csv("hw8_data.csv", check.names = FALSE)
```

## Question 1
How many tissue samples are there by donor and what is their disease status?
```{r}
q1 <- select(df, donor, `Tissue`, `Disease Status`)
q1
```

## Question 2
What is the average AND standard deviation values for CD45+ and PBMCs (%CD45) when grouped by disease status and tissue?
```{r}
q2 <- df %>%
  group_by(`Disease Status`, `Tissue`) %>%
  summarize(Avg = mean(`PBMCs (%CD45)`), St_Dev = sd(`PBMCs (%CD45)`)) %>%
  arrange(desc(`Disease Status`))
q2
```

## Question 3
What is the mean difference between the Eosinophil populations between the different disease statuses, irrespective of tissue?
```{r}

```

## Question 4
When stratified by tissue and disease status, which donors have the highest CD8 Tem CD69+ proportions?
```{r}

```

## Question 5
What are the average AND standard deviation values for all columns that start with “CD4 Tem” when grouped by disease status and tissue?
```{r}

```




